Ordinal bhsdtr tutorial

### 2020-02-18 ordinal/Readme.Rmd
grammar

The meaning is different, because an arbitrary device is not yet an
autonomous purposeful agent. In particular, the sense in which an
arbitrary device "does" something i different than the sense in which
a participant does something. To be a bit more precise, an arbitrary
device does not *try* to do something, it just so happens that it was
designed by an autonomous purposeful agent (one of us) to solve the
problem faced by that agent, but it is the agent who "does all the
trying". This layer of abstraction has to do with behavior, purpose,
and function.

It is only at this layer of abstraction that a mechanism becomes a
*psychological* mechanism. It is my belief that it may be possible to
formalize the process of inference at this level of abstraction. If
such a formal theory of psychological inference was to be discovered,
it would perhaps resemble an abstract theory of agents, tasks, and
cognitive functions. Rational analysis (J.R. Anderson) and
probabilistic models of cognition (Chater, Oaksford, Tenenbaum,
Griffiths, etc) seem to be promising starting points, as does the
Reinforcement Learning framework (Sutton and Barto) in which, to my
knowledge, the first promising weak (a good thing), formal definition
of purposeful action (i.e., of behavior) was proposed, inspired by the
writings of Tolman and Perry. There were times when saw that the
number of free parameters prevents us from answering certain valid and
important questions. By identifying the limits of optimal purposeful
action, this kind of analysis may sometimes significantly lower the
number of free parameters in the models of psychological processes.

>>>>

The meaning is different, because an arbitrary device is not yet an
autonomous purposeful agent. In particular, the sense in which an
arbitrary device "does" something is different than the sense in which
a participant does something. To be a bit more precise, an arbitrary
device does not *try* to do something, it just so happens that it was
designed by an autonomous purposeful agent (one of us) to solve the
problem faced by that agent, but it is the agent who "does all the
trying". This layer of abstraction has to do with behavior, purpose,
and function.

It is only at this layer of abstraction that a mechanism becomes a
*psychological* mechanism. It is my belief that it may be possible to
formalize the process of inference at this level of abstraction. If
such a formal theory of psychological inference was to be discovered,
it would perhaps resemble an abstract theory of agents, tasks, and
cognitive functions. Rational analysis (J.R. Anderson) and
probabilistic models of cognition (Chater, Oaksford, Tenenbaum,
Griffiths, etc) seem to be promising starting points, as does the
Reinforcement Learning framework (Sutton and Barto) in which, to my
knowledge, the first promising weak (a good thing), formal definition
of purposeful action (i.e., of behavior) was proposed, inspired by the
writings of Tolman and Perry. There were times when we saw that the
number of free parameters prevents us from answering certain valid and
important questions. By identifying the limits of optimal purposeful
action, this kind of analysis may sometimes significantly lower the
number of free parameters in the models of psychological processes.
